The Impact of Alternation

### 2017-05-02 draft.tex
ok

>>>>

\section{Predicate Abstraction for Emptiness}

Unlike the boolean closure properties, showed to be effectively
decidable (Lemma \ref{lemma:closure}), the emptiness problem is
undecidable, even in very simple cases. For instance, if $\Data^\I$ is
the set of positive integers, an ADA can simulate an Alternating
Vector Addition System with States (AVASS) \cite{LazicSchmitz14} using
only atoms $x = \overline{x} + k$, for $k \in \nat$ and $x \teq 0$,
with the classical interpretation of function symbols on
integers. Since reachability of a configuration $(q,\nu)$, where $q$
is a control state and $\nu$ a valuation of the variables, is
undecidable, the emptiness problem is undecidable for ADA, in general.

We thus turn to semi-algorithms for this problem and develop methods
that are supposed to be both: \begin{compactenum}
\item \emph{sound}: given an automaton $\A$, if $L(\A) \neq\emptyset$,
  the procedure will terminate and return a word $w \in L(\A)$), and
%
\item \emph{complete relative to termination}: if the procedure terminates
  without returning such a word, then $L(\A) = \emptyset$. 
\end{compactenum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv} \bibliography{refs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
